Syntax and Semantics of Abstract Binding Trees

### 2015-12-12 paper.tex
Add brief acknowledgement
Fix up facile proof

@@

  To prove that the above diagram is a pullback, it suffices to show that for
  any $\Member{m_i}{X(C_i)}$ and $\Member{m_j}{X(C_j)}$ such that
  $\IsEq{X(s_i)(m_i)}{X(s_j)(m_j)}$, we have a unique $\Member{m}{X(C)}$; the
  universal property of the pullback follows immediately from this.

  Consider the singleton cover on $C$ that contains $\Define{h}{s_i\circ
  f_i}=\OMode{s_j\circ f_j}$; a matching family $\phi$ for the cover
  $\MkSet{h}$ is a map that takes $h$ to an object in $X(D)$, and an
  amalgamation for $\phi$ consists in an object $\Member{m}{X(C)}$ such that
  $\IsEq{\phi(h)}{X(h)(m)}$. Now recall that $X$ is a sheaf on $\SCtxSite$ if
  and only if every matching family has a unique amalgamation; for the matching
  family $\Define{\phi(h)}{X(s_i)(m_i)}$, then, we must have a unique amalgamation
  $\Member{m}{X(C)}$ since $X$ is a sheaf. Therefore, $X$ preserves pullbacks.

>>>>

\section*{Acknowledgements}

The first author wishes to thank Robert Harper for numerous conversations about
abstract binding trees and symbolic parameters, and Andy Pitts for his help in
understanding multi-sorted nominal sets and atomic sheaves.

@@

  We have to show that $X(C)$ is, up to equivalence, the pullback of $X(s_j)$
  along $X(s_j)$ in $\Sets$, namely:
  \[
    \IMode{X(C_i)\times_{X(D)}X(C_j)}
      \cong
    \OMode{
      \MkSet{
        (m_i, m_j)\in X(C_i)\times X(C_j)
          \mid
        m_i \cdot s_i = m_j \cdot s_j
      }
    }
  \]
  The first direction of the equivalence is trivial: for each
  $\Member{m}{X(C)}$, we can easily exhibit $\Member{(m\cdot f_i,m\cdot
  f_j)}{X(C_i)\times_{X(D)}X(C_j)}$.

  For the other direction, fix $\Member{(m_i,
  m_j)}{X(C_i)\times_{X(D)}X(C_j)}$.  Consider the singleton cover on $C$ that
  contains $\Define{h}{s_i\circ f_i}=\OMode{s_j\circ f_j}$; a matching family
  $\phi$ for the cover $\MkSet{h}$ is a map that takes $h$ to an object in
  $X(D)$, and an amalgamation for $\phi$ consists in an object
  $\Member{m}{X(C)}$ such that $\IsEq{\phi(h)}{X(h)(m)}$. Now recall that $X$
  is a sheaf on $\SCtxSite$ if and only if every matching family has a unique
  amalgamation; for the matching family $\Define{\phi(h)}{m_i\cdot
  s_i}=\OMode{m_j\cdot s_j}$, then, we must have a unique amalgamation
  $\Member{m}{X(C)}$ since $X$ is a sheaf. Therefore, $X$ preserves pullbacks.
